Fitting convex polyhedra to project 2D bounding box

### 2015-09-28 Paper/supplementarymaterial.tex
Added explanation for computing better projection of 3D ellipsoid.

\subsection{System of equations}
Let the detected bounding box be represented by $[\xmin, \ymin, \xmax, \ymax]^T$. Let $^cT_t$ be the transformation from tracklet to camera.
\newcommand{\Cu}{C_u}
\newcommand{\Cc}{C_c}
\begin{align}
  \Cu &= \begin{bmatrix}
    0.5 & 0.5 & 0\\
    0.5 & -0.5 & 0\\
    -0.5 & -0.5 & 0\\
    -0.5 & 0.5 & 0\\
    0.5 & 0.5 & 1\\
    0.5 & -0.5 & 1\\
    -0.5 & -0.5 & 1\\
    -0.5 & 0.5 & 1
  \end{bmatrix}\\
  C_i &= \diag( C_{u\{i,:\}} ) \begin{bmatrix}3& 0\\0 & 1 \\1 & 0\end{bmatrix} 
\end{align}

@@

\section{Numerical integration}
Numerical integration is possible by computed by sampling. Samples need to be
generated from the association probability $\assocP$ for a given $j$. We take
proposal distribution to be a GMM with modes around probable reflection points.
The weights of all Gaussians in the mixture are proportional to the distance of
the point $j$ from projection of ellipsoid centre i.e. 
\begin{align}
  A_{ij} = \frac{1}{Z_j}\exp(-(\trackpj{t} - \mu^i_u)^\top\Sigma_u^i(\trackpj{t} - \mu^i_u))
\end{align}
where $Z_j = \sum_{i=1}^N A_{ij}$ and $\mu^i_u$ and $\Sigma_u^i$ are described in \eqref{eq:muiudef} and \eqref{eq:sigmauidef} respectively.
The range of Gaussian $G_i$
must be in the interval $[\|\relp{i}{t}\|, \|\relp{i}{t}\| -
\sqrt{3}\max(\dimsn{i})]$. Hence we take the mean as $\|\relp{i}{t}\| -
\frac{\sqrt{3}}{2}\max(\dimsn{i})$ and variance as
$\frac{1}{3}\max(\dimsn{i})^2$. The distribution from which we sample is 
\begin{align}
  \PropDist(\lambda) = \sum_i A_{ij} \Gauss(\lambda; \|\relp{i}{t}\| -
  \frac{\sqrt{3}}{2}\max(\dimsn{i}), \frac{1}{\sqrt{3}}\max(\dimsn{i}))
\end{align}
And the numerical integral with $K$ samples is computed by
\begin{align}
    \int_1^{\infty}
    \assocP
    \Ereproj(\lambda)
    d\lambda
    =
    \frac{1}{K}\sum_k \Ereproj \frac{\assocPk}{\PropDist(\lambda_k)}
\end{align}
where $\lambda_k$ is the $k$th sample drawn from $\PropDist(\lambda)$.

@@

Let $\tcmut = \tctot - \muit$
\begin{align}
  (\Rctot \xc + \tcmut)^\top \Sigmait (\Rctot \xc + \tcmut) = 1
\end{align}
\begin{align}
  \xc^\top \Rctot^\top \Sigmait \Rctot \xc + 2 (\Rctot^\top \tcmut)^\top  \Rctot^\top\Sigmait \Rctot \xc
  + \tcmut^\top \Sigmait \tcmut = 1
\end{align}
Let $\Sigmaic = \Rctot^\top \Sigmait \Rctot$ and $\muic = - \Rctot^\top
\tcmut$
\begin{align}
  (\xc - \muic)^\top\Sigmaic(\xc - \muic) - \muic^\top\Sigmaic\muic +
  \tcmut^\top \Sigmait \tcmut = 1
\end{align}
Let $\Sigmaicf = \frac{\Sigmaic}{1 - \tcmut^\top \Sigmait \tcmut +
\muic^\top\Sigmaic\muic}$
\begin{align}
(\xc - \muic)^\top\Sigmaicf(\xc - \muic) = 1
\end{align}

@@

\section{Projection of ellipsoid to image}
\newcommand{\mubar}{\bar{\mu}_i}
The perspective projection of an ellipsoid in general is not an ellipsoid in
general. We approximate the projection of ellipsoid by projecting a slice
through the ellipsoid. We choose the slice as the plane perpendicular to the
line joining the center of ellipsoid to the optical center of camera. Let
$\muic$ and $\Sigmaicf$ be the parameters of ellipsoid describing the ellipsoid
in camera coordinates. The any point $x$ on the plane satisfies
$x^\top\frac{\muic}{\|\muic\|} = \|\muic\|$. We introduce 
$\mubar = \frac{\muic}{\|\muic\|^2}$ for notational simplicity. Hence, we want
to project the points that satisfy both the equation of chosen plane and the 
ellipsoid i.e.
\begin{align}
  \mubar^\top x = x^\top\mubar &= 1\\ 
  (x-\muic)^\top\Sigmaicf(x-\muic) &= 1 \enspace.
\end{align}
We rewrite $\muic = \muic\mubar^\top x$, and $1 = x^\top\mubar \mubar^\top x$
\begin{align}
  (x-\muic\mubar^\top x)^\top\Sigmaicf(x-\muic\mubar^\top x) &= x^\top\mubar \mubar^\top x \enspace,
\end{align}
which is equivalent to 
\begin{align}
  x^\top\left((I-\muic\mubar^\top)^\top\Sigmaicf(I-\muic\mubar^\top) - \mubar \mubar^\top\right)x &= 0\enspace.
\end{align}

Note that if $u$ is a projection of $x$ to camera with intrinsic parameters
$K$, then $x = K^{-1}u$ where $u$ is in homgeneous coordinates. Hence the above equation can be re-written as
\newcommand{\Sproj}{\Sigma^{-1}_{\text{proj }i}}
\newcommand{\Sperpcut}{\Sigma^{-1}_{\text{perpcut }i}}
\begin{align}
  u^\top\Sproj u &= 0\enspace, 
\end{align}
where $\Sproj = K^{-\top}\Sperpcut K^{-1}$ and 
\begin{align}
  \Sperpcut = (I-\muic\mubar^\top)^\top\Sigmaicf(I-\muic\mubar^\top) - \mubar \mubar^\top \enspace.
\end{align}

@@

  \section{Uncertainty addition in measurement}
  Consider that we have a set of measurements whose mean and variance are known $\mu = E(x)$ and $\Sigma = E ((x - \mu_x)(x - \mu_x)^\top)$. We want to know the
  affect of uncertainty on mean and variance of existing observations. On adding
  noise $[\Delta x, \Delta y]^\top$ with zero mean and covariance $\Delta
  \Sigma = E(\Delta x \Delta x^\top)$ the covariance of new data is given by
  \begin{align}
    E((x + \Delta x)(x+\Delta x)^\top) = E(xx^\top) + E(x \Delta x^\top) %\\
    + E(\Delta x x^\top) + E(\Delta x \Delta x^\top)
  \end{align}
  where the terms $E(x \Delta x^\top)$ denote the correlation between the data
  vector and the uncertainty in the data. Although we understand that in our case
  the data is the appearance based detection score and uncertainty because of
  occlusion is closely related to the appearance and hence detection score, we
  assume independence between $x$ and $\Delta x$. Hence our resultant covariance
  matrix $ E((x + \Delta x)(x+\Delta x)^\top) = \Sigma + \Delta \Sigma$
  are 4D. But that should not be a problem because the detection scores are
  modeled as $[x_{\text{min}}, y_{\text{min}}, x_{\text{max}},
  y_{\text{max}}]^\top$, we can stack the vectors in the soft occlusion region
  domain as the regions are independent of min or max variation. The parameters
  of 4D occlusion distribution are given by

>>>>

\subsection{System of equations}
Let the detected bounding box be represented by $B$. Let $^cT_t$ be the transformation from tracklet to camera.
\newcommand{\Cu}{C_u}
\newcommand{\Cc}{C_c}
\begin{align}
  B &= [\xmin, \ymin, \xmax, \ymax]^T
  \\
  \Cu &= \begin{bmatrix}
    0.5 & 0.5 & 0\\
    0.5 & -0.5 & 0\\
    -0.5 & -0.5 & 0\\
    -0.5 & 0.5 & 0\\
    0.5 & 0.5 & 1\\
    0.5 & -0.5 & 1\\
    -0.5 & -0.5 & 1\\
    -0.5 & 0.5 & 1
  \end{bmatrix}\\
  C_i &= \diag( C_{u\{i,:\}} ) \begin{bmatrix}3& 0\\0 & 1 \\1 & 0\end{bmatrix} 
\end{align}

@@

\section{Numerical integration}
Numerical integration is possible by computed by sampling. Samples need to be
generated from the association probability $\assocP$ for a given $j$. We take
proposal distribution to be a GMM with modes around probable reflection points.
The weights of all Gaussians in the mixture are proportional to the distance of
the point $j$ from projection of ellipsoid centre i.e. 
\begin{align}
  A_{ij} = \frac{1}{Z_j}\exp(-(\trackpj{t} - \mu^i_u)^\top\Sigma_u^i(\trackpj{t} - \mu^i_u))
\end{align}
where $Z_j = \sum_{i=1}^N A_{ij}$ and $\mu^i_u$ and $\Sigma_u^i$ are described in %\eqref{eq:muiudef} and \eqref{eq:sigmauidef} respectively.
The range of Gaussian $G_i$
must be in the interval $[\|\relp{i}{t}\|, \|\relp{i}{t}\| -
\sqrt{3}\max(\dimsn{i})]$. Hence we take the mean as $\|\relp{i}{t}\| -
\frac{\sqrt{3}}{2}\max(\dimsn{i})$ and variance as
$\frac{1}{3}\max(\dimsn{i})^2$. The distribution from which we sample is 
\begin{multline}
  \PropDist(\lambda) = \sum_i A_{ij} \\
  \Gauss(\lambda; \|\relp{i}{t}\| -
  \frac{\sqrt{3}}{2}\max(\dimsn{i}), \frac{1}{\sqrt{3}}\max(\dimsn{i}))
\end{multline}
And the numerical integral with $K$ samples is computed by
\begin{align}
    \int_1^{\infty}
    \assocP
    \Ereproj(\lambda)
    d\lambda
    =
    \frac{1}{K}\sum_k \Ereproj \frac{\assocPk}{\PropDist(\lambda_k)}
\end{align}
where $\lambda_k$ is the $k$th sample drawn from $\PropDist(\lambda)$.

@@

Let $\tcmut = \tctot - \muit$
\begin{align}
  (\Rctot \xc + \tcmut)^\top \Sigmait (\Rctot \xc + \tcmut) = 1
\end{align}
\begin{multline}
  \xc^\top \Rctot^\top \Sigmait \Rctot \xc + 2 (\Rctot^\top \tcmut)^\top  \Rctot^\top\Sigmait \Rctot \xc
  \\
  + \tcmut^\top \Sigmait \tcmut = 1
\end{multline}
Let $\Sigmaic = \Rctot^\top \Sigmait \Rctot$ and $\muic = - \Rctot^\top
\tcmut$
\begin{multline}
  (\xc - \muic)^\top\Sigmaic(\xc - \muic) - \muic^\top\Sigmaic\muic 
  \\
  + \tcmut^\top \Sigmait \tcmut = 1
\end{multline}
Let $\Sigmaicf = \frac{\Sigmaic}{1 - \tcmut^\top \Sigmait \tcmut +
\muic^\top\Sigmaic\muic}$
\begin{align}
(\xc - \muic)^\top\Sigmaicf(\xc - \muic) = 1
\end{align}

@@

\section{Projection of ellipsoid to image}
\newcommand{\mubar}{\bar{\mu}_i}
The perspective projection of an ellipsoid in general is not an ellipsoid in
general. We approximate the projection of ellipsoid by projecting a slice
through the ellipsoid.

\subsection{Tangent planes method}
\newcommand{\nx}{\hat{n}_x}
We chose the slice as the plane passing through the four points that touch 
the tangent planes through the origin.
Let the normal to plane representing $\xmin$, $\xmax$ be $\nx = [\cot(\alpha),
0, 1]^\top$. The tangent point lies on the plane, ellipsoid and at
the tangent point the gradient of ellipsoid is parallel to the plane normal.
%
\begin{align}
  x^\top \nx = \nx^\top x &= 0\\
  (x-\muic)^\top\Sigmaicf(x-\muic) &= 1 \\
  2\Sigmaicf (x - \muic) &= \lambda \nx \enspace .
\end{align}%
%
Eliminating $x$ from the three equations we get,
%
\begin{align}
  \frac{ \lambda^2 }{ 4 } \nx^\top \Sigmaicfinv \nx &= 1\\
  \frac{ \lambda }{ 2 } \nx^\top \Sigmaicfinv \nx - \muic^\top \nx &= 0
\end{align}%
%
Solving for $\lambda$ we get $\lambda = \frac{ 2 \muic^\top \nx }{ \nx^\top \Sigmaicfinv \nx }$ or
%
\begin{align}
  \nx^\top \muic \muic^\top \nx &= \nx^\top \Sigmaicfinv \nx\\
  \nx^\top (\Sigmaicfinv - \muic \muic^\top) \nx &= 0
\end{align}%
%
Let $C := \Sigmaicfinv - \muic \muic^\top$ and the quadratic equation can be solved by
%
\begin{align}
  \cot(\alpha) &= \frac{ - C_{13} \pm \sqrt{ C^2_{13} - C_{11}C_{33} } }{ C_{11}  }
\end{align}%
%
Similarly for $\beta_y$

\begin{align}
  \cot(\beta) &= \frac{ - C_{23} \pm \sqrt{ C^2_{23} - C_{22}C_{33} } }{ C_{22}  }
\end{align}%

%
\begin{align}
  \lambda &= \frac{ 2 } { [\cot(\alpha), 0, 1] \muic}\\
  x &= \frac{ 1 } { [\cot(\alpha), 0, 1] \muic } \Sigmaicfinv [\cot(\alpha), 0, 1]^\top + \muic
\end{align}%
%
Once we have four such points $[x_1, x_2, x_3, x_4]$, we can solve for the plane which is given by the null space of $A = \begin{bmatrix}
  x_1^\top & 1\\
  x_2^\top & 1\\
  x_3^\top & 1\\
  x_4^\top & 1
\end{bmatrix}$
\newcommand{\np}{\hat{n}_p}
Let $\np$ be the normal of the derived plane such that the equation of plane is $\np^\top x = 1$.

\subsection{Perpendicular plane method}
 We choose the slice as the plane perpendicular to the
line joining the center of ellipsoid to the optical center of camera. Let
$\muic$ and $\Sigmaicf$ be the parameters of ellipsoid describing the ellipsoid
in camera coordinates. The any point $x$ on the plane satisfies
$x^\top\frac{\muic}{\|\muic\|} = \|\muic\|$. We introduce 
$\np = \mubar = \frac{\muic}{\|\muic\|^2}$ for notational simplicity. Hence, we want
to project the points that satisfy both the equation of chosen plane and the 
ellipsoid i.e.

\subsection{Projection of the ellipsoid slice}
\begin{align}
  \np^\top x = x^\top\np &= 1\\ 
  (x-\muic)^\top\Sigmaicf(x-\muic) &= 1 \enspace.
\end{align}
We rewrite $\muic = \muic\np^\top x$, and $1 = x^\top\np \np^\top x$
\begin{align}
  (x-\muic\np^\top x)^\top\Sigmaicf(x-\muic\np^\top x) &= x^\top\np \np^\top x \enspace,
\end{align}
which is equivalent to 
\begin{align}
  x^\top\left((I-\muic\np^\top)^\top\Sigmaicf(I-\muic\np^\top) - \np \np^\top\right)x &= 0\enspace.
\end{align}

Note that if $u$ is a projection of $x$ to camera with intrinsic parameters
$K$, then $x = K^{-1}u$ where $u$ is in homgeneous coordinates. Hence the above equation can be re-written as
\newcommand{\Sproj}{\Sigma^{-1}_{\text{proj }i}}
\newcommand{\Sperpcut}{\Sigma^{-1}_{\text{perpcut }i}}
\begin{align}
  u^\top\Sproj u &= 0\enspace, 
\end{align}
where $\Sproj = K^{-\top}\Sperpcut K^{-1}$ and 
\begin{align}
  \Sperpcut = (I-\muic\np^\top)^\top\Sigmaicf(I-\muic\np^\top) - \np \np^\top \enspace.
\end{align}
If $u = [v^\top, 1]^\top$, $A = \Sproj(1:2, 1:2)$, $b = \Sproj(1:2, 3)$, $b^\top = \Sproj(3, 1:2)$ and $d = \Sproj(3,3)$ the equation can be expanded as
%
\begin{align}
[v^\top, 1]\begin{bmatrix} A & b\\ b^\top & d \end{bmatrix}[v^\top, 1]^\top &= 0\\
v^\top A v + 2 b^\top v + d &= 0
\end{align}
\begin{multline}
  v^\top A v + 2 b^\top A^{-\top} A v + b^\top A^{-\top} A A^{-1}b \\
  = b^\top A^{-\top} b - d
\end{multline}
\begin{multline}
  \left(v + A^{-1} b\right)^\top A \left( v + A^{-1} b\right) \\
  = b^\top A^{-\top}b - d
\end{multline}%
%
The mean and sigma of the projected ellipse can be computed by

%
\begin{align}
  \mu_{\text{2D}} &= A^{-1} b\\
  \Sigma^{-1}_{\text{2D}} &= \frac{1}{b^\top A^{-\top} b - d} A
\end{align}%
%

@@

  \section{Uncertainty addition in measurement}
  Consider that we have a set of measurements whose mean and variance are known $\mu = E(x)$ and $\Sigma = E ((x - \mu_x)(x - \mu_x)^\top)$. We want to know the
  affect of uncertainty on mean and variance of existing observations. On adding
  noise $[\Delta x, \Delta y]^\top$ with zero mean and covariance $\Delta
  \Sigma = E(\Delta x \Delta x^\top)$ the covariance of new data is given by
  \begin{multline}
    E((x + \Delta x)(x+\Delta x)^\top) = E(xx^\top) + E(x \Delta x^\top) 
    \\
    + E(\Delta x x^\top) + E(\Delta x \Delta x^\top)
  \end{multline}
  where the terms $E(x \Delta x^\top)$ denote the correlation between the data
  vector and the uncertainty in the data. Although we understand that in our case
  the data is the appearance based detection score and uncertainty because of
  occlusion is closely related to the appearance and hence detection score, we
  assume independence between $x$ and $\Delta x$. Hence our resultant covariance
  matrix $ E((x + \Delta x)(x+\Delta x)^\top) = \Sigma + \Delta \Sigma$
  are 4D. But that should not be a problem because the detection scores are
  modeled as $[x_{\text{min}}, y_{\text{min}}, x_{\text{max}},
  y_{\text{max}}]^\top$, we can stack the vectors in the soft occlusion region
  domain as the regions are independent of min or max variation. The parameters
  of 4D occlusion distribution are given by
